Parsing Tweets into Universal Dependencies

### 2018-04-15 paper.tex
section 3

%	\begin{tabular}{rrrrrr}
%		\hline
%		\multicolumn{2}{l}{version} & train & dev & test & total \\
%		\hline
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
%	\end{tabular}
\caption{Statistics of {\sc Tweebank v2} and the comparison with
{\sc Tweebank v1} in quantity.
%\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
%I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
%\yjcomment{i've fix this.}
\label{tbl:data-stat}
}
\end{table}
Our annotation process was conducted in two stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
portion and the additional 210 tweets and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the general UD
annotation conventions and our guidelines specifically for annotating tweets.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and a
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\footnote{Manual annotation was done with Arborator \cite{gerdes:2013:W13-37}, a web platform for drawing dependency trees.}
Newly created annotations are split into train, development, and test sets and appended
to the original splits of {\sc Twebank v1}. Statistics of our annotations and data splits are shown
in Table~\ref{tbl:data-stat}.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 97.3 \\
		 Twokenizer & 94.6 \\
% 		UDPipe v1.2 & 94.7 \\
		\hdashline
		UDPipe v1.2 & 97.4 \\
	 	our bi-LSTM tokenizer & 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
%on combined training data affect our decision about how to tokenize.} trained 
%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
%outperforms the one trained only on the dialect treebank.  
Our preliminary results
showed that our model trained on
the combination of UD\_English-EWT and Tweebank v2
outperforms the one trained only on the UD\_English-EWT or Tweebank v2,
which also was confirmed by previous works on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
So we trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English-EWT training set
and tested on the \textsc{Tweebank v2} test set. % \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} are rule-based systems and were not adapted
to the UD tokenization scheme.
The UDPipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with UDPipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 vs.~20),
which has stronger representation power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.%\nss{this paragraph needs copyediting}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.6 \\
%		UDPipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 93.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 94.6 \\
		\hdashline
%		UDPipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 92.5 \\
%		our word bi-LSTM & 89.2 \\
%		our character + word bi-LSTMs & 91.5 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
\end{table}

@@

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. The careful feature engineering and making use of
\citet{Brown:1992:CNG:176313.176316} clusters in the 
POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citeposs{ma-hovy:2016:P16-1} neural network
model. 
%tagger
%also makes use of clusters derived
%from a large collection of unannotated tweets. % Those clusters did not
%improve the performance of our bi-LSTM models.)

@@

In our preliminary experiments, we train our parser on the combination of UD\_English-EWT
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters %, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score (including punctuation) are reported.
All the experiments were run on a Xeon E5-2670 2.6 GHz machine.

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \Citeposs{kong-EtAl:2014:EMNLP2014} parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses the biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Learning from exploration.} When we set $\alpha =1$, we
eliminate the oracle from the estimation procedure (for the distilled
model).  This presents an opportunity to learn with \emph{exploration}, by
randomly sampling transitions from the ensemble, found useful
in recent methods for training greedy models that use dynamic oracles
\citet{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
We find that this
approach outperforms the  conventional distillation model, coming in
only one point behind the ensemble (last line of Table~\ref{tbl:parse-result}).

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.

>>>>

%	\begin{tabular}{rrrrrr}
%		\hline
%		\multicolumn{2}{l}{version} & train & dev & test & total \\
%		\hline
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
%	\end{tabular}
\caption{Statistics of {\sc Tweebank v2} and the comparison with
{\sc Tweebank v1} in quantity.
%\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
%I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
%\yjcomment{i've fix this.}
\label{tbl:data-stat}
}
\end{table}
Our annotation process was conducted in two stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
portion and the additional 210 tweets and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the general UD
annotation conventions and our guidelines specifically for annotating tweets.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and a
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\footnote{Manual annotation was done with Arborator \cite{gerdes:2013:W13-37}, a web platform for drawing dependency trees.}
Newly created annotations are split into train, development, and test sets and appended
to the original splits of {\sc Tweebank v1}. Statistics of our annotations and data splits are shown
in Table~\ref{tbl:data-stat}.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 97.3 \\
		 Twokenizer & 94.6 \\
% 		UDPipe v1.2 & 94.7 \\
		\hdashline
		UDPipe v1.2 & 97.4 \\
	 	our bi-LSTM tokenizer & 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
%on combined training data affect our decision about how to tokenize.} trained 
%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
%outperforms the one trained only on the dialect treebank.  
Our preliminary results
showed that our model trained on
the combination of UD\_English-EWT and \textsc{Tweebank v2}
outperformed the one trained only on the UD\_English-EWT or \textsc{Tweebank v2},
consistent with previous work on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
So we trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English-EWT training set
and tested on the \textsc{Tweebank v2} test set. % \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} are rule-based systems and were not adapted
to the UD tokenization scheme.
The UDPipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with UDPipe, we use an LSTM
instead of a GRU in our model and we also use a larger size for hidden units (64 vs.~20),
which has stronger representational power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results speak to the value of statistical modeling
in tokenization for informal texts.%\nss{this paragraph needs copyediting}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & Precision\nss{Accuracy?} \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.6 \\
%		UDPipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 93.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 94.6 \\
		\hdashline
%		UDPipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 92.5 \\
%		our word bi-LSTM & 89.2 \\
%		our character + word bi-LSTMs & 91.5 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
\end{table}

@@

We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
with gold-standard tokenization are shown in
Table \ref{tbl:pos-result}. Careful feature engineering and 
\citet{Brown:1992:CNG:176313.176316} clusters  
help \citeposs{owoputi-EtAl:2013:NAACL-HLT} feature-based POS taggers to outperform \citeposs{ma-hovy:2016:P16-1} neural network
model. 
%tagger
%also makes use of clusters derived
%from a large collection of unannotated tweets. % Those clusters did not
%improve the performance of our bi-LSTM models.)

@@

In our preliminary\nss{initial?} experiments, we train our parser on the combination of UD\_English-EWT
and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
tags are used. Automatic POS tags are assigned with 5-fold
jackknifing. Hyperparameters %, including the value of $\alpha$ in Equation \ref{eq:distill},
are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
labeled attachment score (including punctuation) are reported.
All the experiments were run on a Xeon E5-2670 2.6 GHz machine.

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \Citeposs{kong-EtAl:2014:EMNLP2014} parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses a biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Learning from exploration.} When we set $\alpha =1$, we
eliminate the oracle from the estimation procedure (for the distilled
model).  This presents an opportunity to learn with \emph{exploration}, by
randomly sampling transitions from the ensemble, found useful
in recent methods for training greedy models that use dynamic oracles
\citep{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
We find that this
approach outperforms the  conventional distillation model, coming in
only one\nss{UAS? LAS is 1.5 points} point behind the ensemble (last line of Table~\ref{tbl:parse-result}).

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than\nss{? 77.9 vs. 74.0, right?} four points.
